Merge_MCGrowthData

### 2024-01-17 Code/Merge_MCGrowthData.Rmd
Added an intro and removed the pivot longer for GAM data frame. Structured the data frame in the PICOgam.Rmd.

---
title: "MultiDataGrowthAssessPico"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Douglas A. Campbell
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

# Introduction

# Materials and Methods

## Load Libraries and set project variables

```{r load libraries, message= TRUE}
# libraries; Note check actual dependencies

@@

# Read .Rds, Summarize, Combine to single data frame. Create function using to read in .Rds, adding source filename as a column
```{r readRDS_plus}
readRDS_plus <- function(Flnm){readRDS(file = Flnm) %>%
    mutate(Filename = Flnm)
}
```

@@

#Fix ExpStartTime such that only time is extracted
```{r fix start time column}
LogFitsData <- LogFitsData %>%
   mutate(ExpStartTime = hms::as_hms(ymd_hms(ExpStartTime)))

@@

```{r combine unnested fits}

@@

```{r, pivot Nested data longer for GAM}

# OD720 pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
Pivot_Longer_OD720_est <- MCGrowthFits %>%
  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,  OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept
            )) %>%
   pivot_longer(c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# OD720 pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
Pivot_Longer_OD720_se <- MCGrowthFits %>%
  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,   OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se
            )) %>%
   pivot_longer(c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

# Join OD720 estimate and se DF 
Longer_OD720_Joined <- full_join(Pivot_Longer_OD720_est, Pivot_Longer_OD720_se)

remove(Pivot_Longer_OD720_est, Pivot_Longer_OD720_se)

# rename common columns for full join
Longer_OD720_Joined <- Longer_OD720_Joined %>%
  rename(GrowthAmp_14days = 'GrowthAmpOD720_14days',
         GrowthAmp_14daysFlag = 'GrowthAmpOD720Flag_14days',
         Lmu_seFlag = 'OD720_LseGrowthFlag',
         Lmutrunc_seFlag = 'OD720trunc_LseGrowthFlag'
         )

# deltaOD pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
Pivot_Longer_deltaOD_est <- MCGrowthFits %>%
  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept
            )) %>%
   pivot_longer(c( deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# deltaOD pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
Pivot_Longer_deltaOD_se <- MCGrowthFits %>%
  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se
            )) %>%
   pivot_longer(c(deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

# Join deltaOD estimate and se DF 
Longer_deltaOD_Joined <- full_join(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)

remove(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)

# rename common columns for full join
Longer_deltaOD_Joined <- Longer_deltaOD_Joined %>%
  rename(GrowthAmp_14days = 'GrowthAmpdeltaOD_14days',
         GrowthAmp_14daysFlag = 'GrowthAmpdeltaODFlag_14days',
         Lmu_seFlag = 'deltaOD_LseGrowthFlag',
         Lmutrunc_seFlag = 'deltaODtrunc_LseGrowthFlag'
         )

#Join OD720 and deltaOD fits data
LongerFitsData <- rbind(Longer_OD720_Joined, Longer_deltaOD_Joined) %>%
  mutate_if(is.numeric, round, digits = 3)

remove(Longer_OD720_Joined, Longer_deltaOD_Joined)

glimpse(LongerFitsData)

```
# Remove redundant df
```{r remove}
remove(LogFitsData)
```

@@

saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "LongerGrowthFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

>>>>

---
title: "Merge_MCGrowthData"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Douglas A. Campbell
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

# Introduction
This Rmd, "Merge_MCGrowthData", reads in all individually processed MultiCulti runs from the "\Data\ProcessedData\ProcessedMCData" folder and merges the data into 1 data frame. Growth estimate flags are defined based on absolute amplitude change. Growth estimates are set to 0 for models that returned a negative growth estimate and if the absolute amplitude change threshold was not met. For conditions that were replicated, a mean growth estimate was calculated. This single data frame is saved as a .Rds for further analysis called "PICO_Processed_MCGrowthFits.Rds" in the "\Data\CleanData\CleanedMCData" folder.

# Load Libraries and set project variables
```{r load libraries, message= TRUE}
# libraries; Note check actual dependencies

@@

# Create function using to read in .Rds, adding source filename as a column. Read .Rds, summarize, combine to single data frame. 
```{r readRDS_plus}
readRDS_plus <- function(Flnm){readRDS(file = Flnm) %>%
    mutate(Filename = Flnm)
}
```

@@

#Fix ExpStartTime to extract only time 
```{r fix start time column}
LogFitsData <- LogFitsData %>%
   mutate(ExpStartTime = hms::as_hms(ymd_hms(ExpStartTime)))

@@

# Merge OD720 with deltaOD fits
```{r combine unnested fits}

@@

# Remove redundant df
```{r remove}
remove(LogFitsData)
```

@@
